---
title: "R Notebook"
output: html_notebook
---

Use defensive programming techniques to make the function calc_sum_stat more robust.

```{r}
calc_sum_stat <- function(df, cols) {
  df_sub <- df[, cols, drop = FALSE]
  sum_stat <- apply(df_sub, 1, mean)
  return(sum_stat)
}
```

Some specific ideas:

* Assert that the input df is not empty (hint: use dim)
* Assert that cols is a character vector
* Assert that the columns listed in cols are in df (hint: use %in% and colnames)
* Assert that df_sub is a data frame (hint: use is.data.frame)
* Assert that sum_stat is not NA
* Issue a warning if cols only contains one column (since taking the mean of one column isn’t very useful, the user may have made a mistake)

```{r}
calc_sum_stat <- function(df, cols) {
  stopifnot(dim(df) != c(0,0), is.character(cols), cols %in% names(df))
  if (length(cols) == 1) {
    warning("taking the mean of one column may not be very useful")
    cat("\n")
  }
  df_sub <- df[, cols, drop = FALSE]
  stopifnot(is.data.frame(df_sub))
  sum_stat <- apply(df_sub, 1, mean)
  stopifnot(!is.na(sum_stat))
  return(sum_stat)
}
```



```{r}
set.seed(123)
dn <- data.frame(a = rnorm(5,1), b = rnorm(5,1), c = rnorm(5,1))
calc_sum_stat(dn, "a")
# calc_sum_stat(dn, 1)  [1] 0.4395244 0.7698225 2.5587083 1.0705084 1.1292877
# calc_sum_stat(dn, 2)  [1] 2.7150650  1.4609162 -0.2650612  0.3131471  0.5543380
```

```{r}
set.seed(123)
dn <- data.frame(a = rnorm(5,1), b = rnorm(5,1), c = rnorm(5,1))
calc_sum_stat(dn, c("a", "b"))
# calc_sum_stat(dn, 1)  [1] 0.4395244 0.7698225 2.5587083 1.0705084 1.1292877
# calc_sum_stat(dn, 2)  [1] 2.7150650  1.4609162 -0.2650612  0.3131471  0.5543380
```


```{r}
set.seed(123)
dn <- data.frame(a = rnorm(5,1), b = rnorm(5,1), c = rnorm(5,1))
calc_sum_stat(dn, 1)
# calc_sum_stat(dn, 1)  [1] 0.4395244 0.7698225 2.5587083 1.0705084 1.1292877
# calc_sum_stat(dn, 2)  [1] 2.7150650  1.4609162 -0.2650612  0.3131471  0.5543380
```
